Context Aware Virtual Assistant with Case-Based Conflict Resolution in Multi-User Smart Home Environment

### 2018-01-06 Report/test.tex
First commit of Paper.

        on user cases. As a result, a Case-Based Reasoning algorithm was created with an innovative Ospan Matrix distance
        measurement module. In addition, Feed-Forward Artificial Neural Networks were used to classify user inputs, voice

@@

    metadata [11]. As a consequence, majority of the researches is aimed to develop systems that helps alone living users.
    \\Despite number of

@@

    specific out-of-rule situations. \\To sum up

@@

    there is a lack of the Virtual Assistants with an adaptive conflict resolution systems. \\

@@

    Home devices. Finally, the VA has to manage to resolve conflicts between multiple users, and adapt to the new user cases.
    \\To cover all objectives, we introduced and developed the VA with next modules. Firstly, we have developed user friendly

@@

    different variates of the user commands and argumentation sentences. Therefore, users were able to speak to

@@

    in performing an action, analyzes via Ospan Matrix distance k-nearest neighbour (kNN) algorithm similarities between
    this case and previous cases and chooses best-fit case. In other words, VA asks user to say why he or she wants to change

@@

    arguments and previous cases.
    \\Furthermore, we have established randomized double-blinded evaluation tests. In order to perform randomized double

@@

    testers are positive and only weak place of the system is accent recognition task.
    \\This paper presents Virtual Assistant in the multiple user Smart Home environment. The architecture of the system is
    described in the Section II. The system algorithms and sequences are described in the Section III. Section IV demonstrates
    our results and validation. Finally, Section V draws the conclusion and predictions for the future work.
    \section{Architecture}
    There will be architecture.
    \subsection{Graphical User Interface}
    Gui is described here.
    \subsection{Dialogue Component}
    All about ANNs and dialogue manager.
    \subsection{Rule-Based Reasoner}
    \subsection{Case-Based Reasoner}
    \subsection{Device Control Unit}
    \section{Sequences}
    There is sequence diagram.
    \subsection{Regular Scenario}
    \subsection{Conflict Scenario}
    \section{Results and Validation}
    \section{Conclusion and Future Work}
    \section{References}
    \label{refer}
    There are three reference systems available; only one, of course,
    should be used for your contribution. With each system (by
    number only, by letter-number or by author-year) a reference list
    containing all citations in the
    text, should be included at the end of your contribution placing the
    \LaTeX{} environment \verb|thebibliography| there.
    For an overall information on that environment
    see the {\em \LaTeX{} User's Guide \& Reference
    Manual\/} by Leslie Lamport, p.~71.

    There is a special {\sc Bib}\TeX{} style for LLNCS that works along
    with the class: \verb|splncs.bst|
    -- call for it with a line \verb|\bibliographystyle{splncs}|.
    If you plan to use another {\sc Bib}\TeX{} style you are customed to,
    please specify the option \verb|[oribibl]| in the
    \verb|documentclass| line, like:
    \begin{verbatim}
        \documentclass[oribibl]{llncs}
    \end{verbatim}
    This will retain the original \LaTeX{} code for the bibliographic
    environment and the \verb|\cite| mechanism that many {\sc Bib}\TeX{}
    applications rely on.
    %
    \subsection{References by Letter-Number or by Number Only}
    %
    References are cited in the text -- using the \verb|\cite|
    command of \LaTeX{} -- by number or by letter-number in square
    brackets, e.g.\ [1] or [E1, S2], [P1], according to your use of the
    \verb|\bibitem| command in the \verb|thebibliography| environment. The
    coding is as follows: if you choose your own label for the sources by
    giving an optional argument to the \verb|\bibitem| command the citations
    in the text are marked with the label you supplied. Otherwise a simple
    numbering is done, which is preferred.
    \begin{verbatim}
        The results in this section are a refined version
        of \cite{clar:eke}; the minimality result of Proposition~14
        was the first of its kind.
    \end{verbatim}
    The above input produces the citation: ``\dots\ refined version of
    [CE1]; the min\-i\-mality\dots''. Then the \verb|\bibitem| entry of
    the \verb|thebibliography| environment should read:
    \begin{verbatim}
        \begin{thebibliography}{[MT1]}
            .
            .
            \bibitem[CE1]{clar:eke}
            Clarke, F., Ekeland, I.:
            Nonlinear oscillations and boundary-value problems for
            Hamiltonian systems.
            Arch. Rat. Mech. Anal. 78, 315--333 (1982)
            .
            .
        \end{thebibliography}
    \end{verbatim}
    The complete bibliography looks like this:
    %
    \begin{thebibliography}{[MT1]}
        %
        \bibitem[CE1]{clar:eke}
        Clarke, F., Ekeland, I.:
        Nonlinear oscillations and
        boundary-value problems for Hamiltonian systems.
        Arch. Rat. Mech. Anal. 78, 315--333 (1982)
        %
        \bibitem[CE2]{clar:eke:2}
        Clarke, F., Ekeland, I.:
        Solutions p\'{e}riodiques, du
        p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
        Note CRAS Paris 287, 1013--1015 (1978)
        %
        \bibitem[MT1]{mich:tar}
        Michalek, R., Tarantello, G.:
        Subharmonic solutions with prescribed minimal
        period for nonautonomous Hamiltonian systems.
        J. Diff. Eq. 72, 28--55 (1988)
        %
        \bibitem[Ta1]{tar}
        Tarantello, G.:
        Subharmonic solutions for Hamiltonian
        systems via a $\bbbz_{p}$ pseudoindex theory.
        Annali di Matematica Pura (to appear)
        %
        \bibitem[Ra1]{rab}
        Rabinowitz, P.:
        On subharmonic solutions of a Hamiltonian system.
        Comm. Pure Appl. Math. 33, 609--633 (1980)
    \end{thebibliography}
    %
    \subsubsection*{Number-Only System.}
    %
    For this preferred system do not use the optional argument
    in the \verb|\bibitem| command: then, only numbers will
    appear for the citations in the text (enclosed in square brackets)
    as well as for the marks in your
    bibliography (here the number is only end-punctuated without
    square brackets).

    Subsequent citation numbers in the text are collapsed to ranges.
    Non-numeric and undefined labels are handled correctly but no sorting is
    done.

    E.g., \verb|\cite{n1,n3,n2,n3,n4,n5,foo,n1,n2,n3,?,n4,n5}| -- where
    \verb|n|$x$ is the key of the $x^{\mathrm{th}}$ \verb|\bibitem|
    command in sequence, \verb|foo| is the key of a \verb|\bibitem| with an
    optional argument, and \verb|?| is an undefined reference -- gives
    1,3,2-5,foo,1-3,?,4,5 as the citation reference.

    \begin{verbatim}
        \begin{thebibliography}{1}
            \bibitem {clar:eke}
            Clarke, F., Ekeland, I.:
            Nonlinear oscillations and boundary-value problems for
            Hamiltonian systems.
            Arch. Rat. Mech. Anal. 78, 315--333 (1982)
        \end{thebibliography}
    \end{verbatim}
    %
    \subsection{Author-Year System}
    %
    References are cited in the text by name and year in parentheses
    and should look as follows:
    (Smith 1970, 1980), (Ekeland et al. 1985, Theorem 2), (Jones and Jaffe
    1986; Farrow 1988, Chap.\,2). If the name is part of the sentence
    only the year may appear in parentheses,
    e.g.\ Ekeland et al. (1985, Sect.\,2.1)
    The reference list should contain all citations occurring in the text,
    ordered alphabetically by surname (with initials following). If there
    are several works by the same author(s) the references should be listed
    in the appropriate order indicated below:
    \begin{alpherate}
        \setlength{\hfuzz}{5pt}
        \item
        One author: list works chronologically;
        \item
        Author and same co-author(s): list works chronologically;
        \item
        Author and different co-authors: list works alphabetically
        according to co-authors.
    \end{alpherate}
    If there are several works by the same author(s) and in the same year,
    but which are cited separately, they should be distinguished by the use
    of ``a'', ``b'' etc., e.g.\ (Smith 1982a), (Ekeland et al. 1982b).
    %
    \subsubsection*{How to Code Author-Year System.}
    %
    If you want to use this system you have to specify the option
    \verb|[citeauthoryear]| in the \verb|documentclass|, like:
    \begin{verbatim}
        \documentclass[citeauthoryear]{llncs}
    \end{verbatim}
    Write your citations in the text explicitly except for the year, leaving
    that up to \LaTeX{} with the \verb|\cite| command. Then give only the
    appropriate year as the optional argument (i.e. the label in square
    brackets) with the \verb|\bibitem| command(s).\\[2mm]
    {\itshape Sample Input}
    \begin{verbatim}
        The results in this section are a refined version
        of Clarke and Ekeland (\cite{clar:eke}); the minimality result of
        Proposition~14 was the first of its kind.
    \end{verbatim}
    The above input produces the citation: ``\dots\ refined version of
    Clarke and Ekeland (1982); the minimality\dots''. Then the
    \verb|\bibitem| entry of \verb|clar:eke| in the \verb|thebibliography|
    environment should read:
    \begin{verbatim}
        \begin{thebibliography}{}  % (do not forget {})
            .
            .
            \bibitem[1982]{clar:eke}
            Clarke, F., Ekeland, I.:
            Nonlinear oscillations and boundary-value problems for
            Hamiltonian systems.
            Arch. Rat. Mech. Anal. 78, 315--333 (1982)
            .
            .
        \end{thebibliography}
    \end{verbatim}
    {\itshape Sample Output}
    \bibauthoryear
    %
\end{document}

>>>>

        on user cases. As a result, a Case-Based Reasoning algorithm was created with a k-Nearest Neighbor classification algorithm.
        In addition, Feed-Forward Artificial Neural Networks were used to classify user inputs, voice

@@

    metadata [11]. As a consequence, majority of the researches is aimed to develop systems that helps alone living users.\\
    Despite number of

@@

    specific out-of-rule situations. \\
    To sum up

@@

    there is a lack of the Virtual Assistants with an adaptive conflict resolution systems.
    \section{Methodology}

@@

    Home devices. Finally, the VA has to manage to resolve conflicts between multiple users, and adapt to the new user cases.\\
    To cover all objectives, we introduced and developed the VA with next modules. Firstly, we have developed user friendly

@@

    different variates of the user commands and argumentation sentences, because they are effective algorithms for
    sentence classification [19]. Therefore, users were able to speak to

@@

    in performing an action, analyzes via k-nearest neighbour (kNN) algorithm similarities between
    this case and previous cases and chooses best-fit case [4,7,15]. In other words, VA asks user to say why he or she wants to change

@@

    arguments and previous cases. Futhermore, arguments priorities was established by personal user preferences [3] because
    number of researches shows that the preference-based argumentation increases ability of the systems to meet user
    expectations [5].
    \section{Validation}
    Furthermore, we have established randomized double-blinded evaluation tests. In order to perform randomized double

@@

    testers are positive and only weak place of the system is accent recognition task.\\
    This paper presents Virtual Assistant in the multiple user Smart Home environment. The Virtual Assistant was created
    to manage and monitor Smart Home environment by dialogue based interaction with users. Different machine learning
    algorithms and cloud technologies were implemented to meet project objectives. The main focus of the research was to
    develop adaptive conflict resolution system based on Case-Based Reasoner. The validation tests feedback is positive.
    The future direction of the work is to implement context-aware system that analyzes user behaviour and reports it as
    a case to the database of Case-Based Reasoner.

    \section{References}
    \bibliographystyle{llncs}
    \bibliography{./bib.bib}

\end{document}
